Does a fully convective star need a special corona to produce a polar flare?

### 2023-06-30 src/tex/ms.tex
[showyourwork] overleaf sync

\subsection{Spectral fitting}

@@

From the proposal: $F_X=2.7^{-13}$ erg/s/cm$^2$, $L_X=6\cdot10^27$ erg/s (update with new eROSITA data) -- 1 oom above the measured XMM values.
\begin{table*}
% \movetableright=-20mm
\footnotesize
    \script{TABLE_specfits.py}
    \caption{XSPEC fits to PN, MOS1/MOS2 and joint data also.}
    \input{output/specfit.tex}
        \label{tab:specfit}
\end{table*}

@@

APEC+APEC model, grsa abundances

>>>>

\subsection{Spectral fitting}
We fitted a two-temperature VAPEC+VAPEC model to the joint PN and MOS spectra, using solar abundances from GRSA, but adjusting to an Fe/0=.6 ratio, which is more typical of M dwarfs. An APEC+APEC model leads to similar results with a XXXX Chi-square value.

@@

% From the proposal: $F_X=2.7^{-13}$ erg/s/cm$^2$, $L_X=6\cdot10^27$ erg/s (update with new eROSITA data) -- 1 oom above the measured XMM values.
\begin{table*}
% \movetableright=-20mm
\footnotesize
    \script{TABLE_specfits.py}
    \caption{XSPEC fits to PN, MOS1/MOS2 and joint data also.}
    \input{output/specfit.tex}
        \label{tab:specfit}
\end{table*}

@@
